### 2014-02-11 msc-thesis/chapters/4/chapter-discussion.tex
MSC Added changes to thesis.

While each study presented in this dissertation is quite unique, this chapter will focus on the underlying themes and
results of all 4 studies. This chapter will address the usefulness of the results presented towards academia and
what those results mean for continued studies in future research as well as discuss how the results can be viewed
for larger over arching outcomes than those presented in results sections.

@@

As we have seen through Study 1, developers which are tied to source code objects can become a focal point of
indirect conflicts through the life of a project. For instance we can see from Table~\ref{tab:ratio} that
developers Daniel and Anne on Hibernate-ORM are always linked indirect conflicts when dependencies between
their source code objects change. This is an important observation to make when moving forward with indirect
conflicts.

@@

The question of how to prevent this type of negative impact is ultimately the goal of indirect conflicts. Study 1 has
shown that pairs of developers can often be a large component to that goal as well. (Impact from Study 2 was
created the address just this issue.)

\textbf{Information Overload} \textit{My tool Impact, as well as many other indirect conflict tools, suffer from
information overload in their delivery to developers which is a key issue in preventing adopting and acceptance
of indirect conflict tools.}

As was previously stated, many indirect conflict tools end up suffering from information overload to developers
and other end users. Impact was initially created to take the knowledge learned from Study 1 and attempt to create
a new indirect conflict system based on developer interactions inside the code base which would potentially address
information overload. However, we now know from the results of Study 2, that Impact once again suffered defeat to information
overload based on the case study evaluation. Ultimately, this sense of information overload ends up causing
adoption of indirect conflict tools to fail which in turn causes some research components to have failed as
well.

@@

While the previous section discussed the main motivations for taking a step back on indirect conflicts in order to understand
better what can be done to improve developer work flow, this section will discuss exactly those steps back. From Studies 3 and
4 we will notice 3 main trends that have been discovered for indirect conflicts in both industry and in academia. These 3 major
trends to now be discussed are: unwanted awareness, prevention versus cure, and the gap in software evolution analysis. This
section will also include a brief discussion regarding the implications, learned from studies 3 and 4, for both academia and
for industry through tools.

@@

\textbf{Prevention versus Cure} \textit{The largest implication for future research found in this paper is the need for continued study of the open question
``Which of prevention or cure is more effective for software development and indirect conflicts?''. This simple question will undoubtedly 
produce extremely complex answers.}

@@

\textbf{Awareness Theory to Model Real World} \textit{the need to further characterize the
mismatch between awareness approaches and tools as developed in the research community and awareness needs as perceived
by industry. We should push our awareness theories to model real development
environments where interruptions, time management, and full development life cycles are often large factors.}

@@

The more indirect implication of this research on tool creation is that of improving existing tools. While not all existing
tools are used for indirect conflicts alone (automatic debugging~\cite{Zeller:2005:WPF}, unit tests, etc), most of these tools
have need for rapid expansion, according to developers, for dealing with indirect conflicts. The ability to have unit tests
automatically written for a given software object's contract, the ability to find a change  in an external project
which has broken a developer's own project, or any automation of the existing detection and resolution stages of indirect
conflicts are what developers currently seek. But of course, most of these implications rely on the improvement of 
static analysis tools.

>>>>

While each study presented in this dissertation is quite unique, this chapter will focus on the underlying themes and
results of all 4 studies. This chapter will address the usefulness of the results presented towards the
research community and
what those results mean for continued studies in future research as well as discuss how the results can be viewed
for larger over arching outcomes than those presented in results sections.

@@

As we have seen in Study 1, developers which are tied to source code objects can become a focal point of
indirect conflicts through the life of a project. For instance we can see from Table~\ref{tab:ratio} that
developers Daniel and Anne on Hibernate-ORM are always linked indirect conflicts when dependencies between
their source code objects change. This is an important observation to make when moving forward with indirect
conflicts.

@@

The question of how to prevent this type of negative impact is ultimately the goal of indirect conflicts. Study 1 has
shown that pairs of developers can often be a large component to that goal as well. (Impact from Study 2 was
created to use these pairs of developers in addressing the issue of indirect conflicts.)

\textbf{Information Overload} \textit{My tool Impact, as well as many other indirect conflict tools, suffer from
information overload in their delivery to developers which is a key issue in preventing adoption and acceptance
of indirect conflict tools.}

As was previously stated, many indirect conflict tools end up suffering from information overload to developers
and other end users. Impact was initially created to take the insights from Study 1 and attempt to create
a new indirect conflict system based on developer interactions inside the code base which would potentially address
information overload. However, we now know from the results of Study 2, that Impact once again suffered defeat to information
overload based on the case study evaluation. Ultimately, this sense of information overload ends up causing
adoption of indirect conflict tools to fail which in turn causes some research components to have failed as
well.

@@

While the previous section discussed the main motivations for taking a step back on indirect conflicts in order to understand
better what can be done to improve developer work flow, this section will discuss exactly those steps back. From Studies 3 and
4 we will notice 3 main trends that have been discovered for indirect conflicts in both industry and in academia. These 3 major
trends are: unwanted awareness, prevention versus cure, and the gap in software evolution analysis. This
section will also include a brief discussion regarding the implications, learned from studies 3 and 4, for both academia and
for industry through tools.

@@

\textbf{Prevention versus Cure} \textit{The largest implication for future research found in this dissertation is the need for continued study of the open question
``Which of prevention or cure is more effective for software development and indirect conflicts?''. This simple question will undoubtedly 
produce extremely complex answers.}

@@

\textbf{Awareness Theory to Model Real World} \textit{the need to further characterize the
mismatch between awareness approaches and tools as developed in the research community, compared to awareness needs as perceived
by industry. We should push our awareness theories to model real development
environments where interruptions, time management, and full development life cycles are often large factors.}

@@

The more indirect implication of this research on tool creation is that of improving existing tools. While not all existing
tools are used for indirect conflicts alone (automatic debugging~\cite{Zeller:2005:WPF}, unit tests, etc), most of these tools
have a need for rapid expansion, according to developers, for dealing with indirect conflicts. The ability to have unit tests
automatically written for a given software object's contract, the ability to find a change  in an external project
which has broken a developer's own project, or any automation of the existing detection and resolution stages of indirect
conflicts are what developers currently seek. But of course, most of these implications rely on the improvement of 
static analysis tools.
